---
title: "Covid19 Paraná - BR"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    social: menu
    source_code: embed
    vertical_layout: fill
---

```{r setup, include=FALSE}
library(flexdashboard)

#------------------ Parameters ------------------
# Set colors
# https://www.w3.org/TR/css-color-3/#svg-color
confirmed_color <- "purple"
active_color <- "#1f77b4"
recovered_color <- "forestgreen"
death_color <- "red"


#------------------ Data ------------------
library(dplyr)
load("coronavirus.RData")


df <- coronavirus %>% 
#  dplyr::filter(date == max(date)) %>%
  dplyr::group_by(Province.State, type) %>%
  dplyr::summarise(total = sum(cases)) %>%
  tidyr::pivot_wider(names_from =  type, 
                     values_from = total) %>%
  dplyr::arrange(-confirmed) %>%
  dplyr::ungroup() 

df$Province.State=factor(df$Province.State,levels = c(as.character(df$Province.State)))



#head(df)

df_daily <- coronavirus %>% 
  dplyr::group_by(date, type) %>%
  dplyr::summarise(total = sum(cases, na.rm = TRUE)) %>%
  tidyr::pivot_wider(names_from = type,
                     values_from = total) %>%
  dplyr::arrange(date) %>%
  dplyr::ungroup() %>%
  dplyr::mutate(confirmed_cum = cumsum(confirmed),
                death_cum = cumsum(death))


df1 <- coronavirus %>% dplyr::filter(date == max(date))

```


Resumo
=======================================================================
  Row
-----------------------------------------------------------------------

### Confirmados {.value-box}


```{r}
valueBox(value = paste(format(sum(df$confirmed), big.mark = ","), "", sep = " "), 
         caption = "Total de casos confirmados no Paraná", 
         icon = "fas fa-user-md", 
         color = confirmed_color)
```

### Mortos {.value-box}


```{r}

valueBox(value = paste(format(sum(df$death, na.rm = TRUE), big.mark = ","), " (",
                       round(100 * sum(df$death, na.rm = TRUE) / sum(df$confirmed), 1), 
                       "%)", sep = ""),
         caption = "Total de mortes no Paraná (mortalidade %)", 
         icon = "fas fa-heart-broken", 
         color = death_color)
```


Row
-----------------------------------------------------------------------
  
### Casos por cidades (top 30)

```{r daily_summary}

plotly::plot_ly(data = df[1:20,], 
                x = ~ Province.State, 
                y = ~ confirmed, 
                # text =  ~ confirmed, 
                # textposition = 'auto',
                type = "bar", 
                name = "Active",
                marker = list(color = active_color)) %>%
  plotly::add_trace(y = ~ death, 
                    # text =  ~ death, 
                    # textposition = 'auto',
                    name = "Death",
                    marker = list(color = death_color)) %>%
  plotly::layout(barmode = 'stack',
                 yaxis = list(title = "Total de Casos"),
#                              type = "log"),
                 xaxis = list(title = ""),
                 hovermode = "compare",
                 margin =  list(
                   # l = 60,
                   # r = 40,
                   b = 10,
                   t = 10,
                   pad = 2))

```

Row {data-width=400}
-----------------------------------------------------------------------


### Daily Cumulative Cases by Type

```{r}
plotly::plot_ly(data = df_daily) %>%
  plotly::add_trace(x = ~ date,
                    y = ~ confirmed_cum,
                    type = "scatter",
                    mode = "lines+markers",
                    name = "Confirmados",
                    line = list(color = confirmed_color),
                    marker = list(color = confirmed_color)) %>%
  plotly::add_trace(x = ~ date,
                    y = ~ death_cum,
                    type = "scatter",
                    mode = 'lines+markers',
                    name = "Mortes",
                    line = list(color = death_color),
                    marker = list(color = death_color)) %>%
  plotly::layout(title = "",
                 yaxis = list(title = "Acumulado de casos (PR)"),
                 xaxis = list(title = "Data"),
                 legend = list(x = 0.1, y = 0.9),
                 hovermode = "compare")
```



Map
=======================================================================

 **Map**
 
```{r}

 
library(leaflet)
library(leafpop)
library(purrr)


cv_data_for_plot <- coronavirus %>% 
  dplyr::filter(cases > 0) %>% 
  dplyr::group_by(Country.Region,Province.State,Lat,Long,type) %>% 
  dplyr::summarise(cases = sum(cases)) %>% 
  dplyr::mutate(log_cases = 2 * log(cases)) %>% 
  dplyr::ungroup()

cv_data_for_plot.split <- cv_data_for_plot %>% split(cv_data_for_plot$type)
pal <- colorFactor(c("orange", "red"), domain = c("confirmed", "death"))
map_object <- leaflet() %>% addProviderTiles(providers$Stamen.Toner)

names(cv_data_for_plot.split) %>%
  purrr::walk( function(df) {
    map_object <<- map_object %>%
      addCircleMarkers(data=cv_data_for_plot.split[[df]],
                       lng=~Long, lat=~Lat,
                       #                 label=~as.character(cases),
                       color = ~pal(type),
                       stroke = FALSE,
                       fillOpacity = 0.8,
                       radius = ~log_cases,
                       popup =  leafpop::popupTable(cv_data_for_plot.split[[df]],
                                                    feature.id = FALSE,
                                                    row.numbers = FALSE,
                                                    zcol=c("type","cases","Province.State")),
                       group = df,
                       #                 clusterOptions = markerClusterOptions(removeOutsideVisibleBounds = F),
                       labelOptions = labelOptions(noHide = F,
                                                   direction = 'auto'))
  })
map_object %>%
  addLayersControl(
    overlayGroups = names(cv_data_for_plot.split),
    options = layersControlOptions(collapsed = FALSE) 
  )

```



Sobre
=======================================================================


**Coronavirus Paraná Dashboard**

Esse dashboard apresenta as atualizações diárias de casos de Covid19 do estado do Paraná. Este dashboard foi construido no software R utilizando o script do Rmarkdown. 

The code behind the dashboard available [here](https://github.com/RamiKrispin/coronavirus_dashboard)

**Data**

Todos os dados utilizados nesse dashboard foram/são coletados diariamente no portal  [Brasil em dados abertos](https://brasil.io/home). 




**Agradecimentos**

* Prof. Thiago Gentil Ramires -
[UTFPR - Apucarana](https://portal.utfpr.edu.br/)
*Prof. Ana Julia Righetto - 
[UEL](https://ufsc.br/)
*Prof. Luiz Ricardo Nakamura -
[UFSC](https://ufsc.br/)


**Deployment and reproducibly**

The dashboard was deployed to Github docs. If you wish to deploy and/or modify the dashboard on your Github account, you can apply the following steps:

* Fork the dashboard [repository](https://github.com/RamiKrispin/coronavirus_dashboard), or
* Clone it and push it to your Github package
* Here some general guidance about deployment of flexdashboard on Github page - [link](https://github.com/pbatey/flexdashboard-example)

For any question or feedback, you can either open an [issue](https://github.com/RamiKrispin/coronavirus_dashboard/issues) or contact me on [Twitter](https://twitter.com/Rami_Krispin).

**Contribution** 

The **Map** tab was contributed by [Art Steinmetz](@adababbage) on this [pull request](https://github.com/RamiKrispin/coronavirus_dashboard/pull/1). Thanks Art!


```{r, echo=FALSE}
# Define variable containing url asd
url <- "https://pbs.twimg.com/profile_images/1241088175348613123/NfrGE61E_400x400.jpg"
```

<center><img src="`r url`"></center>

